---
title: "Assignment2"
author: "SRIDHARSHINI"
date: "5 August 2024"
output: html_document
---

{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


###1. In this exercise you will create some simulated data and will fit simple linear regression models to it. Make sure to use set.seed(1) prior to starting part (a) to ensure consistent results.rnorm

####a.	Using the rnorm() function, create a vector, “x”, containing 100 observations drawn from a N(0,1) distribution. This represents a feature, X.

```{r}
set.seed(1)
x = rnorm(100, mean = 0, sd = 1)
```

####b.	Using the rnorm() function, create a vector, “eps”, containing 100 observations drawn from a N(0,0.25) distribution.

```{r}
eps = rnorm(100, mean = 0, sd = 0.25)
eps
```


####c.	Using “x” and “eps”, generate a vector “y” according to the modelY=−1+0.5X+ε.What is the length of the vector “y” ? What are the values of β0 and β1 in this linear model ?

```{r}
y = -1 + 0.5 * x + eps
length_y <- length(y)
beta0 <- -1
beta1 <- 0.5
beta1
```
 
####d.	Create a scatterplot displaying the relationship between “x” and “y”. Comment on what you observe.

```{r}
plot(x, y, main = "Scatterplot of X vs Y", xlab = "X", ylab = "Y")
```



####e.	Fit a least squares linear model to predict “y” using “x”. Comment on the model obtained. How do β^0 and β^1 compare to β0 and β1 ?

```{r}
model <- lm(y ~ x)
summary(model)
```



####f.	Display the least squares line on the scatterplot obtained in (d). Draw the population regression line on the plot, in a different color. Use the legend() function to create an appropriate legend.

```{r}
plot(x, y, main = "Scatterplot of X vs Y with Regression Lines", xlab = "X", ylab = "Y")
abline(model, col = "blue")  # Least squares line
abline(a = -1, b = 0.5, col = "red")  # Population regression line
legend("topleft", legend = c("Least Squares Line", "Population Regression Line"), col = c("blue", "red"), lty = 1)
```
```{r}
library(MASS)
library(ISLR)
?Boston
```

```{r}
fit <- lm(crim ~ zn, data = Boston)
summary(fit)
```
```{r}
plot(fit)
```
```{r}
model_all <- lm(crim ~ ., data = Boston) 
plot(model_all)
```

